Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-03-12 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
Tiny edit

{\color{blue} For small sized datasets ($n\lesssim 1000$), HSGPs are likely to be slower than exact GPs already for highly to moderated wiggly $3$D functions (e.g., $\ell_1 \lesssim 0.1$, and $\ell_2, \ell_3 \gtrsim 0.3$) and for overall smooth $4$D functions (e.g., $\ell_1 \lesssim 0.1$, and $\ell_2, \ell_3, \ell_4 \gtrsim 0.4$).}

>>>>

{\color{blue} For small sized datasets ($n\lesssim 1000$), HSGPs are likely to be slower than exact GPs already for moderate to highly wiggly $3$D functions (e.g., $\ell_1 \lesssim 0.1$, and $\ell_2, \ell_3 \gtrsim 0.3$) and for overall smooth $4$D functions (e.g., $\ell_1 \lesssim 0.1$, and $\ell_2, \ell_3, \ell_4 \gtrsim 0.4$).}
